\documentclass[12pt,a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage[margin=2.5cm]{geometry}
\usepackage{natbib}
\usepackage{hyperref}
\usepackage{cleveref}
\usepackage{setspace}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{float}

\onehalfspacing

\title{External Shock Transmission to Hong Kong Under the Currency Board:\
Macro-Econometric Evidence from VAR and VECM}
\author{Steven Chung}
\date{\today}

\begin{document}
\maketitle

\begin{abstract}
This note asks how US monetary conditions and China growth shocks transmit to
Hong Kong's real economy under the currency board. I estimate a quarterly
macro-econometric system for 1998Q1--2026Q1 using official Hong Kong data,
US federal funds rates, China real GDP growth, and Hong Kong exports to the
Chinese Mainland. The baseline is a seven-variable external-first VAR selected
by BIC; a VECM is used as a long-run robustness check because the data show
cointegration among the nonstationary variables.

The current baseline results give a simple interpretation. China real activity
and the Hong Kong export channel matter for real activity: at the eight-quarter
horizon, exports to the Chinese Mainland explain 24.9\% of Hong Kong GDP growth
forecast error variance, while China GDP explains 16.1\%. The US channel is
clearest in interest rates: the federal funds rate explains 53.7\% of HIBOR
variance and 10.6\% of unemployment variance. A rank-2 VECM strengthens the
long-run US rate channel, assigning 65.2\% of HIBOR variance and 47.0\% of
unemployment variance to the US FFR shock. These results are best read as
reduced-form macro-econometric evidence, not as clean causal identification.
Residual autocorrelation remains in several VAR equations, so the strongest
use of the project is as a research note and disciplined forecasting/diagnostic
framework.

\medskip\noindent
\textbf{Keywords:} Hong Kong, currency board, VAR, VECM, FEVD,
monetary transmission, China spillovers, exports

\medskip\noindent
\textbf{JEL Classification:} E32, E52, F41, F42
\end{abstract}

\newpage
\tableofcontents
\newpage

% ==================================================================
\section{Introduction}
\label{sec:intro}
% ==================================================================

Hong Kong's macroeconomic environment is shaped by two external anchors. The
first is monetary: under the Linked Exchange Rate System, Hong Kong imports US
monetary conditions through the HKD--USD currency board. The second is real:
Hong Kong is tightly linked to mainland China through trade, re-exports,
services, and finance. The empirical question is therefore direct: when the US
rate cycle and China growth cycle move, which channel shows up in Hong Kong's
real economy?

This note studies that question with a quarterly VAR/VECM framework. The
baseline system contains seven variables ordered external-first:
\begin{center}
\small
\texttt{us\_ffr}, \texttt{china\_gdp}, \texttt{hk\_exports\_china\_yoy},\\
\texttt{gdp\_growth}, \texttt{cpi\_inflation}, \texttt{unemployment},
\texttt{hibor\_3m}.
\end{center}
This ordering treats the US rate and China activity variables as externally
given within the quarter, allows China activity to affect Hong Kong exports,
and then traces the transmission to Hong Kong GDP, inflation, unemployment, and
HIBOR.

The main findings are:
\begin{enumerate}
    \item \textbf{China transmits through trade and real activity.}
    In the current VAR(1), exports to the Chinese Mainland explain 24.9\% of
    Hong Kong GDP growth variance at the eight-quarter horizon. China real GDP
    growth explains another 16.1\%. This is now a cleaner macro story than the
    earlier version because the model includes an explicit
    China-to-Hong-Kong trade channel.

    \item \textbf{The US channel is mainly an interest-rate channel.}
    The US FFR explains 53.7\% of HIBOR variance in the baseline VAR. It also
    explains 10.6\% of unemployment variance, but only 1.2\% of GDP growth
    variance at the same horizon.

    \item \textbf{VECM strengthens long-run currency-board transmission.}
    Johansen diagnostics select rank 2 for the I(1) subset. In the rank-2 VECM,
    the US FFR explains 65.2\% of HIBOR variance and 47.0\% of unemployment
    variance. This supports the idea that differenced VARs can understate the
    long-run interest-rate comovement created by the peg.

    \item \textbf{The model is useful, but not finished as causal evidence.}
    Residual autocorrelation remains in several VAR equations. The results
    should therefore be described as macro-econometric transmission evidence,
    not as a fully identified structural causal design.
\end{enumerate}

The contribution is practical rather than methodological. The note builds a
transparent quarterly system for Hong Kong, documents the data sources, and
separates the US rate channel from the China real-activity/export channel. The
results are useful for understanding why fiscal and macroprudential instruments
matter in Hong Kong: monetary conditions are imported, while major real shocks
come from external demand that cannot be offset by local interest-rate policy.

% ==================================================================
\section{Literature Review}
\label{sec:literature}
% ==================================================================

This note connects three literatures. First, the small-open-economy VAR
literature studies how foreign interest rates and foreign output transmit to
domestic macro variables \citep{cushman1997identifying,kim2001international}.
The external-first recursive ordering used here follows that logic. Second,
work on sign-restricted VARs emphasizes that recursive timing assumptions are
only one way to discipline structural interpretation \citep{uhlig2005effects,rubio2010structural}.
This project includes sign-restriction diagnostics, but the baseline claims
remain reduced-form. Third, currency-board macroeconomics emphasizes the loss
of domestic monetary autonomy under a hard peg \citep{hanke2002currency}. For
Hong Kong, this means the FFR--HIBOR relationship is not an incidental
correlation; it is part of the monetary regime.

The Hong Kong setting adds a China channel. Prior work on Hong Kong monetary
transmission stresses the importance of US rates for local financial conditions
\citep{genberg2009monetary}, while work on mainland-Hong Kong integration
emphasizes the increasing role of China in Hong Kong's business cycle
\citep{he2014balancing}. This note puts both channels in the same empirical
system and adds exports to the Chinese Mainland as an explicit transmission
variable.

% ==================================================================
\section{Data}
\label{sec:data}
% ==================================================================

\subsection{Variables and Sources}

The current canonical dataset covers 1998Q1--2026Q1, with 113 raw quarterly
observations. The transformed estimation sample has 112 observations because
some variables enter in first differences.

\begin{table}[H]
\centering
\caption{Variable Definitions and Sources}
\label{tab:variables}
\small
\begin{tabular}{@{}p{4.2cm}p{4.8cm}p{1.4cm}p{3.4cm}@{}}
\toprule
Variable & Description & Unit & Source \\
\midrule
\texttt{us\_ffr} & US effective federal funds rate & \% & FRED FEDFUNDS \\
\texttt{china\_gdp} & China real GDP growth & YoY \% & OECD QNA B1GQ, GY \\
\texttt{hk\_exports\_china\_yoy} & HK exports to Chinese Mainland & YoY \% & C\&SD 410-50013 \\
\texttt{gdp\_growth} & HK real GDP growth & YoY \% & C\&SD 310-30001 \\
\texttt{cpi\_inflation} & HK Composite CPI inflation & YoY \% & C\&SD 510-60001 \\
\texttt{unemployment} & HK unemployment rate & \% & C\&SD 210-06101 \\
\texttt{hibor\_3m} & 3-month HIBOR & \% & HKMA API \\
\bottomrule
\end{tabular}
\end{table}

The Hong Kong series come from official Census and Statistics Department
(C\&SD) or HKMA sources. CPI uses the official Composite CPI year-on-year
monthly series from C\&SD table 510-60001, aggregated to quarterly means. The
China variable is documented in the current metadata as OECD QNA real GDP YoY
growth. The code keeps the column name \texttt{china\_gdp} for compatibility;
if the OECD fetch fails in a future rebuild, the fetcher can fall back to FRED
nominal GDP, in which case interpretation must be changed to ``China nominal
activity.'' The current snapshot uses the real-activity interpretation recorded
in \texttt{data/source\_metadata.json}.

\subsection{Stationarity and Cointegration}

I use ADF and KPSS tests jointly. Variables classified as unit-root by the
diagnostic rule are first-differenced for the VAR/BVAR. In the current run,
\texttt{china\_gdp}, \texttt{cpi\_inflation}, and \texttt{unemployment} enter
as first differences. The remaining variables enter in levels:
\texttt{us\_ffr}, \texttt{hk\_exports\_china\_yoy}, \texttt{gdp\_growth}, and
\texttt{hibor\_3m}. The HIBOR tests conflict, so the conservative project rule
keeps it in levels.

Johansen diagnostics on the I(1) subset select rank 2 at the 95\% trace-test
rule after the project cap. The VECM robustness specification therefore uses
rank 2 with a restricted constant. This is economically plausible in a currency
board setting, but the exact VECM interpretation remains sensitive to rank and
deterministic choices.

% ==================================================================
\section{Econometric Framework}
\label{sec:model}
% ==================================================================

\subsection{Estimand and Design}

The estimand is dynamic transmission: the forecast-error contribution of US
monetary conditions, China real activity, and the Hong Kong-China export
channel to Hong Kong GDP growth, CPI inflation, unemployment, and HIBOR. The
baseline design is a reduced-form quarterly VAR with recursive identification
for impulse responses and FEVD. Identification relies on a small-open-economy
ordering assumption: US and China variables do not respond contemporaneously to
Hong Kong macro shocks.

\subsection{VAR Specification}

The reduced-form VAR(\(p\)) is
\[
y_t = c + A_1 y_{t-1} + \cdots + A_p y_{t-p} + u_t,
\qquad u_t \sim (0,\Sigma_u),
\]
where \(y_t\) is the seven-variable vector listed above. BIC selects \(p=1\)
with a low parameter-observation ratio of 0.071. The fitted VAR is stable, with
maximum companion eigenvalue modulus 0.9389. GFC and COVID pulse dummies are
included in the main fit to absorb large event shocks, but residual
autocorrelation remains in several equations and is treated as a limitation.

\subsection{Cholesky Identification}

For FEVD and impulse-response analysis, I decompose \(\Sigma_u = PP'\) using
the external-first ordering. The ordering is
\begin{center}
\small
\texttt{us\_ffr}, \texttt{china\_gdp}, \texttt{hk\_exports\_china\_yoy},\\
\texttt{gdp\_growth}, \texttt{cpi\_inflation}, \texttt{unemployment},
\texttt{hibor\_3m}.
\end{center}
This is a timing restriction, not a full policy-invariant structural model.

\subsection{VECM Robustness}

The VECM is
\[
\Delta y_t = \alpha\beta' y_{t-1} + \sum_{i=1}^{p-1}\Gamma_i\Delta y_{t-i}
+ c + u_t.
\]
It is estimated on level data to preserve long-run relations. In the current
configuration, the VECM uses rank 2 and one lag of differenced terms. It is
reported as long-run robustness because the currency board implies persistent
FFR--HIBOR comovement.

\subsection{FEVD}

The forecast error variance decomposition is
\[
\text{FEVD}_{i,j}(h)=
\frac{\sum_{s=0}^{h}\theta_{ij,s}^2}
{\sum_{s=0}^{h}\sum_{k=1}^{K}\theta_{ik,s}^2}.
\]
The paper reports the eight-quarter horizon because it is long enough to show
transmission while still close to the business-cycle question.

% ==================================================================
\section{Results}
\label{sec:results}
% ==================================================================

\subsection{Baseline Diagnostics}

The canonical run uses
\texttt{python hk\_var\_model.py --lag-criterion bic --model-type var}. The
sample is 1998Q1--2026Q1, BIC selects one lag, and the fitted VAR is stable.
The main diagnostic weakness is residual autocorrelation: Ljung--Box tests at
lag 8 still reject in the US FFR, China GDP, exports-to-China, GDP-growth, and
CPI equations. This does not invalidate the project as a research note, but it
limits strong causal or publication-style claims.

\subsection{Granger-Causality Evidence}

Reduced-form Granger tests line up with the intended channels. China GDP
Granger-causes exports to the Chinese Mainland, Hong Kong GDP growth, CPI
inflation, and unemployment in the transformed system. The US FFR Granger-causes
Hong Kong GDP growth, unemployment, and HIBOR. These tests are predictive
checks, not structural identification, but they support keeping both external
channels in the same system.

\subsection{Forecast Error Variance Decomposition}

\Cref{tab:fevd} reports the central FEVD results at the eight-quarter horizon.
The VAR columns show the baseline seven-variable model. The VECM columns show
the long-run robustness comparison for the US and China shocks.

\begin{table}[H]
\centering
\caption{Forecast Error Variance Decomposition at \(h=8\) Quarters}
\label{tab:fevd}
\small
\begin{tabular}{@{}lccccc@{}}
\toprule
& \multicolumn{3}{c}{VAR(1)} & \multicolumn{2}{c}{VECM rank 2} \\
\cmidrule(lr){2-4} \cmidrule(lr){5-6}
Target & US FFR & China GDP & HK exports & US FFR & China GDP \\
\midrule
HK GDP growth        &  1.2\% & 16.1\% & 24.9\% &  4.2\% & 21.9\% \\
HK CPI inflation     &  0.5\% &  6.6\% &  4.0\% & 20.1\% & 43.2\% \\
HK unemployment      & 10.6\% &  6.3\% &  5.4\% & 47.0\% &  8.6\% \\
3M HIBOR             & 53.7\% &  0.5\% & 10.1\% & 65.2\% &  0.5\% \\
\bottomrule
\end{tabular}
\end{table}

Three results matter. First, the China channel is now best understood as a
combination of China real activity and exports to the Chinese Mainland. For HK
GDP growth, the direct China GDP shock explains 16.1\%, while the export-channel
shock explains 24.9\%. Second, the US channel is concentrated in HIBOR: the FFR
shock explains 53.7\% of HIBOR variance in the VAR. Third, the VECM strengthens
the long-run US channel, especially for unemployment and HIBOR. This is
consistent with the currency-board mechanism, but it should be treated as
robustness rather than a standalone causal estimate.

The exports equation itself is also informative. At the same horizon, own export
shocks explain 77.0\% of exports-to-China variance, while China GDP explains
15.5\%. This suggests that the exports series contains both China-demand content
and Hong Kong-specific trade volatility.

\subsection{Forecast Comparison}

In level-space expanding-window forecast comparison, the VECM wins 18 of 28
RMSE cells against the VAR, while the VAR wins 10. The VECM performs better for
US FFR, China GDP, CPI, and longer-horizon unemployment forecasts. The VAR is
better for exports to China and some GDP/HIBOR horizons. This mixed pattern is
exactly why the paper keeps the VAR as the transparent baseline and the VECM as
long-run robustness.

\subsection{Sign Restrictions and TVP-VAR}

The sign-restriction block accepts 500 rotations out of 50,000 candidate draws
under the current restrictions. Accepted responses are qualitatively consistent
with the economic story: US tightening raises HIBOR and weakens real activity,
while positive China activity shocks support Hong Kong output and prices. These
results are useful as a plausibility check but do not replace the recursive
baseline.

The TVP-VAR block is exploratory. Current residual-standard-deviation checks do
not show it dominating the constant-parameter VAR, so it should not be a main
claim. Its role is to flag possible structural change around the GFC, COVID,
and the recent Fed tightening cycle.

% ==================================================================
\section{Robustness and Limitations}
\label{sec:robustness}
% ==================================================================

\subsection{Ordering and Subsamples}

Ordering robustness and sub-sample checks preserve the broad interpretation:
China and external-demand variables matter more for real activity, while US
rates matter more for HIBOR. The post-GFC period has different coefficient
norms, which is unsurprising given repeated large shocks and shorter effective
sample length.

\subsection{Main Limitations}

The main limitations are straightforward:
\begin{enumerate}
    \item The model is reduced-form. Recursive and sign restrictions impose
    identifying assumptions, but this is not an external-instrument monetary
    shock design.
    \item Residual autocorrelation remains under the BIC-selected VAR(1).
    More lags or BVAR shrinkage can be used as robustness, but they increase
    model complexity.
    \item The China variable must be checked through metadata after each data
    rebuild. In the current snapshot it is OECD real GDP growth; if the fallback
    triggers, it becomes nominal activity and the paper language must change.
    \item Property prices and high-frequency US monetary shock data are useful
    sidecar extensions, but they are not part of the current baseline.
\end{enumerate}

% ==================================================================
\section{Conclusion}
\label{sec:conclusion}
% ==================================================================

This note gives a disciplined answer to the research question. Under the Hong
Kong currency board, US monetary conditions transmit most clearly through the
interest-rate channel: the US FFR explains over half of HIBOR variance in the
baseline VAR, and the VECM raises this share further. China real activity and
exports to the Chinese Mainland matter more for the real economy: together they
account for a substantial share of Hong Kong GDP-growth variance at the
eight-quarter horizon.

The clean interpretation is therefore not ``US versus China'' in a single
ranking. It is channel-specific. US shocks dominate the monetary/interest-rate
channel. China growth and the export channel dominate the real-activity story.
Because Hong Kong imports monetary conditions but faces real shocks from China,
stabilization necessarily relies on fiscal, prudential, and structural policy
rather than independent monetary policy.

The project is now suitable as a macro-econometric research note. The next best
extensions are narrow: use a shorter-sample monetary-surprise series for US
shock robustness, or add property prices only if the question becomes explicitly
macro-financial.

% ==================================================================
\bibliographystyle{apalike}
\bibliography{references}
% ==================================================================

\end{document}
